---
title: "How to extract top 10 values of audio features"
output: html_notebook
---

Download r packages for data wrangling
```{r}
install.packages("dplyr")
library(dplyr)

```

Write the data in
```{r}
d1 <- read.csv("OrangeMergedProsodic_Turns_Transcript.csv")
```

Wrangle the data depending on the audio features
```{r}
# Assuming your_dataset is your dataset and your_variable is the variable you want to rearrange
# target_column is the column based on which you want to rearrange

rearranged_data <- test[order(-test$pd_chunk_median_loudness), ]

```


Since we are working in chunks, we are interested in looking a unique values, so depending on the audio feature rewrite the variable you are interested in investigating
```{r}
# Assuming test is your dataset
unique_top_values <- unique(rearranged_data$pd_chunk_median_loudness)
top_10_unique_values <- head(unique_top_values, 10)

subset_data <- subset(rearranged_data, pd_chunk_median_loudness %in% top_10_unique_values)


```

Since it is extremely important to validate if your script is doing the correct thing, run a plot to confirm if there are 10 unique chunks_ids that are being used
```{r}
# Assuming your_dataset is your dataset
ggplot(subset_data, aes(x = chunk_id)) +
  geom_bar() +
  labs(title = "Frequency of chunk_id Values", x = "Chunk ID", y = "Frequency")


```



